---
title: "Find a Major League Ballpark"
author: "Andy Sullivan"
date: "6/19/2020"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

mlb_ballparks <- data.frame(
    lat = c(33.80029,33.89127,39.283944,42.346561,41.948314,41.829892,39.097213,41.496005,39.756175,42.339063,
            29.757041,39.051604,34.073878,25.778165,43.028232,44.981749,40.757134,40.829586,37.751619,39.906109,
            33.44542,40.446835,32.70753,47.591443,37.778324,38.622622,27.768254,32.7511,43.641256,38.872987),
    long = c(-117.882685,-84.4681,-76.621572,-71.097337,-87.655397,-87.633703,-84.506483,-81.685326,-104.99413,
             -83.048627,-95.355429,-94.480149,-118.239951,-80.219541,-87.970966,-93.278026,-73.84584,-73.926413,
             -122.200451,-75.166485,-112.066793,-80.005683,-117.157056,-122.332283,-122.389221,-90.192841,
             -82.653431,-97.0832,-79.389054,-77.007435),
    league = c('AL','NL','AL','AL','NL','AL','NL','AL','NL','AL','AL','AL','NL','NL','NL','AL','NL','AL','AL',
               'NL','NL','NL','NL','AL','NL','NL','AL','AL','AL','NL'),
    division = c('West','East','East','East','Central',
                 'Central','Central','Central','West','Central',
                 'West','Central','West','East','Central',
                 'Central','East','East','West','East',
                 'West','Central','West','West',
                 'West','Central','East','West','East','East'),
    team = c('Anaheim Angels','Atlanta Braves','Baltimore Orioles','Boston Red Sox','Chicago Cubs',
             'Chicago White Sox','Cincinnati Reds','Cleveland Indians','Colorado Rockies','Detroit Tigers',
             'Houston Astros','Kansas City Royals','Los Angeles Dodgers','Miami Marlins','Milwaukee Brewers',
             'Minnesota Twins','New York Mets','New York Yankees','Oakland As','Philadelphia Phillies',
             'Arizona Diamondbacks','Pittsburgh Pirates','San Diego Padres','Seattle Mariners',
             'San Francisco Giants','St Louis Cardinals','Tampa Rays','Texas Rangers','Toronto Blue Jays',
             'Washington Nationals'),
    info = c('Angel Stadium of Anaheim','SunTrust Park','Oriole Park at Camden Yards','Fenway Park','Wrigley Field',
             'Guarantee Rate Park','Great American Ballpark','Progressive Field','Coors Field','Comerica Park','Minute Maid Park',
             'Kauffman Stadium','Dodger Stadium','Marlins Park','Miller Park','Target Field','Citi Field',
             'New Yankee Stadium','Oakland-Alameda County Coliseum','Citizens Bank Park','Chase Field','PNC Park',
             'Petco Park','T-Mobile Park','Oracle Park','Busch Stadium','Tropicana Field','Globe Life Park',
             'Rogers Centre','Nationals Park'))

library(shiny)
library(leaflet)
```

## Find a Major League Ball Park

Baseball is considered the United States' National Past Time.  During the summer months, many fans of Baseball will travel to many games across the nation.

This application was created to help those travelers find Major League Ballparks.  Application users can select a League or Division to limit their search

## Left Side of Screen

The left side of the screen shows two pull downs to help the user refine their search

- League - There are 3 selections; Both for both leagues, AL for the American League, and NL for the National League
- Division  - There are 4 selections: All for all divisions, East for East Division, Central for Central Division and West for West Division

## Main Section of the Screen

The Main Section shows the results based on the refined search.  The user will see 2 outputs

- A Map that shows all the Major League Ballparks Selected
- A Data table that gives more information about each Major League Ballpark Selected

## Displaying the Ballparks

This is an example of the code used to generate the map

```{r diaplay, echo = TRUE, message=FALSE}
mlb_ballparks %>% 
  leaflet(height=300, width=600) %>%
  addTiles() %>%
  addMarkers(clusterOptions = markerClusterOptions(),
             label = paste(mlb_ballparks$team,',',mlb_ballparks$info))
```

## For more Information

Please visit the application at <https://unrivalledswan.shinyapps.io/ballparks/>

The github repository can be viewed at <https://github.com/UnrivalledSwan/Developing-Data-Products-Week4-Project>

